\begin{abstract}  
    One of the challenging problems of unmanned aerial vehicles (UAVs) is controlling vertical takeoff and landing (VTOL) aircraft.
    VTOL aircraft can take off and land without landing strips while retain the efficiency of fixed-wing airplanes for long range flight.
    Unfortunately, the transition from takeoff and forward flight, and from forward flight to landing, is an extremely difficult control problem.
    Most current controllers for transition switch between flight regimes based solely on airspeed.
    The trajectory for such switching transitions is a straight vertical ascension followed by a straight forward startup flight; it does not allow for the development of more complex trajectories.
    In this thesis, a generalized trajectory tracking controller is developed for a 2D quadplane dynamic model.
    This controller runs continuously between hover and forward flight, but switches from  using an optimization algorithm.
    Using this controller, the quadplane can follow a degree 3 B-Spline trajectory during hover, transition, and fixed-wing flight modes.
    In addition to the controller, several related areas are also explored and developed.
    An aerodynamic coefficient estimator was developed for a fixed-wing vehicle. 
    This estimator may help estimate the aerodynamic model of the quadplane VTOL, which will assist future hardware implementation.
    A B-Spline library was developed for efficiently generating trajectories for all UAVs.
    This library stores sampled basis functions in lookup tables to maximize generation efficiency.
    A variation of the rapidly exploring random trees (RRT) algorithm was developed for planning a path through obstacle-laden environments.
    This variation finds a series of obstacle-free regions known as safe flight corridors (SFCs) and optimizes a B-Spline path through those regions.
    Finally, a quadplane is simulated to follow a trajectory generated by modified RRT algorithm, using the controller developed in the first section.
\end{abstract}
